Compositional equivalences based on Open pNets

### 2020-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
ajout de ref

\ERIC{ To the best of our knowledge, there is no other research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, parameterised, with loops and assignments)
For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches, event though these are not specific to "weak" approaches.}

@@

Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,Dubut:20} --verifier Dubut--, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.

\subsubsection*{Symbolic and data-sensitive systems}
\ERIC{ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al. \cite{HENNESSY:95, Lin:96}. They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late) bisimulations, they also study STGs with assignments which can be a model for message-passing processes. Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (ie congruent), even for the weak version. Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independant systems. }

@@

Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaivour of other processes, like composition operators or interaction 
protocols that synchronize the actions of processes that can be plugged afterwards. Open
pNets are hierarchical composition of automata with holes and parameters. We
defined here a semantics for open pNets and a complete bisimulation theory for them. 
The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy. Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets. To be precise, it is on open automata that we define our bisimulation relations.

>>>>

\ERIC{ To the best of our knowledge, there is no other research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, parameterised, with loops and assignments).
For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches, event though these are not specific to "weak" approaches.}

@@

Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire. \TODO{Logical formulae are suitable formats that  capture the general class of components that can take part in placeholders of the system during its evolution.}

\subsubsection*{Symbolic and data-sensitive systems}
\ERIC{ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al. \cite{HENNESSY:95, Lin:96, IngolfsdottirL:2001}. They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late) bisimulations, they also study STGs with assignments which can be a model for message-passing processes. Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (i.e. congruent), even for the weak version. Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independent systems. }

@@

Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaviour of other processes, like composition operators or interaction 
protocols that synchronize the actions of processes that can be plugged afterwards. Open
pNets are hierarchical composition of automata with holes and parameters. We
defined here a semantics for open pNets and a complete bisimulation theory for them. 
The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy. Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets. To be precise, it is on open automata that we define our bisimulation relations.
